---
title: "stats_practice"
author: "Nicole Jimenez"
date: "2022-10-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("gitcreds")
#install.packages("usethis")

#set github

# usethis::create_github_token()
# #login and make token
# #copy and past token here
# 
# gitcreds::gitcreds_set()
# #Selection : your_token
# 
# 
# #access .r environment
# usethis::edit_r_environ()
# #github path should be token
# 
# #activate git/make prokect repository
# usethis::use_git(message = "adding stats project")

```



```{r}
##set up libraries
library(dplyr)
library(tidyverse)
library(caret)
library(readr)
library(ggplot2)
library(data.table)
```
Load Data
```{r}
##load feature data - species
Cer_vaginal_species_feature <-
  read_csv("C:/Users/nicolejimenez/OneDrive - University of Arizona/Desktop/Atopobium/cervical_cancer_NAU/cervical_cancer_NAU_level_7_taxa_table.csv")
View(Cer_vaginal_species_feature)
```

```{r}
#load metadata check to make sure it is csv not txt!
Cer_AV_vag_meta <- read_csv("C:/Users/nicolejimenez/OneDrive - University of Arizona/Desktop/Atopobium/cervical_cancer_NAU/Cervical_cancer_NAU_metadata_level_7.csv")
View(Cer_AV_vag_meta)
```
Statistical Question:
Does the number of Atopobiaceae species types affect the genital inflammatory score?

Null hypothesis: The number of Atopobiaceae species types does not affect genital inflammatory score
Alternate hypothesis: the number of Atopobiacea species types does affect the genital inflammatory score

```{r , echo=TRUE}
model <- lm(T_infl_score_flt ~ Atopobiaceae_types, data = Cer_AV_vag_meta)
summary(model)$coef
```
genital inflammation = 1.369 + 0.284*Atopobiaceae_species

```{r , echo=TRUE}
ggplot(Cer_AV_vag_meta, aes(x = Atopobiaceae_types, y = T_infl_score_flt)) +
  geom_point() +
  stat_smooth()
```
Since the data is in groups there is no correlation observed, let's try with more true continous variables...
The null hypothesis is not rejected. 


New Statistical Question:
Does the number of BMI affect the genital inflammatory score?

Null hypothesis: The number of BMI does not affect genital inflammatory score
Alternate hypothesis: the number of BMI does affect the genital inflammatory score

```{r , echo=TRUE}
model <- lm(T_infl_score_flt ~ F_pcov_BMI, data = Cer_AV_vag_meta)
summary(model)$coef
```
genital inflammation = 3.356 - 0.052*BMI

```{r , echo=TRUE}
ggplot(Cer_AV_vag_meta, aes(x = F_pcov_BMI
, y = T_infl_score_flt)) +
  geom_point() +
  stat_smooth()
```

In this dataset there is a weak negative correlation observed with genital inflammation score. Meaning women with higher BMI tend to have lower genital inflammation which is counter-intuitive since obesity is associated with systemic inflammation. That said the inflammation level is a score an not based on a true continous variable such as inflammatory cytokine levels. 
The null hypothesis is rejected.